### 2011-05-31 thesis/contents.tex
Changes regarding detection with multiple variables.

\section{Copping with Multiple Novel Variables}
On the previous section it was shown how to detect a novel class on a variable
assuming that the rest of the graph variables and structure hold true with the
knowledge acquired by the agent.

>>>>

\section{Copping with Multiple Novel Variables}
On the previous section it was shown how to detect a novel class on a variable
assuming that the rest of the graph variables and structure is correctly modeled
by the agent knowledge.
But the test to detect a given variable $a$ is novel requires both a structure
$G$ representing the case where no knowledge gaps exist and a structure $U$
representing the case where $a$ was identified as a novel class.

It may be tempting to use a deterministic approach on the system such as:
when the agent determines a variable to have a novel class, it marks it as novel
and proceeds.

Such an approach would no longer be optimal and not be dynamic
executes on a new
structure $U$ 
of the semantic structure it does not allows the
semantic structure to be used
